Gas exchange in large rivers controlled by largest turbulent eddies: implications for remotely sensing gas exchange via SWOT

### 2021-09-09 manuscript_v4.Rmd
big push for reframing as a finding of channel efficiency

---
title: "Gas exchange in large rivers controlled by largest turbulent eddies: implications for remotely sensing gas exchange via SWOT"
author: 'CB Brinkerhoff, CJ Gleason, PA Raymond, MH Harlan'
date: "`r Sys.Date()`"
bibliography: References.bib
csl: agu_citation_style.csl
output:
  word_document: 
      reference_docx: word-styles-reference.docx
---

>>>>

---
title: "Gas exchange in large rivers controlled by largest turbulent eddies: implications for remotely sensing gas exchange via SWOT"
author: 'CB Brinkerhoff, CJ Gleason, CJ Zappa, PA Raymond, MH Harlan'
date: "`r Sys.Date()`"
bibliography: References.bib
csl: agu_citation_style.csl
output:
  word_document: 
      reference_docx: word-styles-reference.docx
---
